Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-06 paper/main.tex
udpates
Updates

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}
\usepackage{fancyvrb}
\usepackage[ruled]{algorithm2e}

@@

@@

\begin{figure}[t!]
	\centering
	\includegraphics[page=1]{fig5.pdf}
	\caption{DAG learned using the adult income dataset using an LLM (GEMINI-1.5-flash) as the expert.}
	\label{fig:adult_llm}
\end{figure}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}
% \usepackage{fancyvrb}
\usepackage[ruled]{algorithm2e}

@@

Using the mixed data measure of association presented in the last section, we 
now present a method to rank modifications to a given DAG.

@@

\begin{figure}[t!]
	\centering
	\includegraphics[page=1]{fig5.pdf}
	\caption{DAG learned using the adult income dataset using an LLM (GEMINI-1.5-flash) as the expert. The p-value threshold used is $ 0.05 $ and the measure of association threshold is $ 0. 1 $}
	\label{fig:adult_llm}
\end{figure}
